---
name: Everett Trechter
position: "Data Analyst, Student of Public Policy"
address: "Hubert Humphrey - University of Minnesota"
phone: 810.931.6633
profilepic: me.jpg
www: www.everettcarytrechter.com
email: "everett.trechter@gmail.com"
twitter: everett_ct
github: Everett-Trechter
linkedin: Everett Trechter
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I am interested in a career centered on research and analysis in the realm of policy,
political sociology and/or organizational sociology. I am currently looking to gain
analytic skills and a more in depth understanding of research methods, theories and
general knowledge in order to comprehend and help correct the structural inequalities
of our world. My degree in Industrial Engineering with a focus on Information Systems
and Computer Science provides a solid foundation of technical skills and experiences
working with data-driven solutions. In my career I have built on those skills and have
used them to help government agencies, hospital organizations, and most recently the
Oce of Admissions and Recruitment at the University of Wisconsin."
output: 
  vitae::awesomecv
headcolor: 77815c

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

#Skills
 * Data Analysis (using R)
 * Data Reporting and Visualization (R, Excel, and Tableau)
 * Geographical Information Systems (QGIS and ArcGIS)
 * Relational Database Design and SQL
 * PeopleSoft Query Tools, PeopleTools, PeopleCode
 * Familiar with Java, HTML/CSS, Javascript, Python, and R
 * Skilled with Microsoft Oce Suite, including VBA Macros and MS Access
 * Troubleshooting and creative problem solving
 * Quick learning, speed reading

# Education
```{r}
tribble(
  ~ degree, ~ uni, ~school, ~ dates, ~ details,
  "Bachelor of Science in Industrial Engineering", "University of Pittsburgh","Swanson School of Engineering","2007 - 2011","Magna Cum Laude"
)%>%
  detailed_entries(degree, dates, uni, school, details)
```

#Experience
```{r}
tribble(
  ~ role, ~ company, ~ dates, ~ details,
  "Senior Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2017 - Present","Represented OAR on various campus committees to help coordinate campus wide
data governance policies",
 "Senior Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2017 - Present","Found various data sources and angles of analysis to direct marketing strategies
to increase applications and enrollment from various populations",
"Senior Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2017 - Present","Continued finding needs and uses for data visualization dashboards throughout
the office",
 "Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2014 - 2017","Supported collection and processing of prospective applicant data.",
 "Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2014 - 2017","Analyzed applicant and recruiting data in reports to support decision making.",
 "Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2014 - 2017","Began use of geographical data and maps for recruitment decision making.",
 "Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2014 - 2017","Developed an inventory tracking database for recruiting supplies.",
 "Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2014 - 2017","Handled many on-going and ad-hoc data requests from campus partners, counselors, and others.",
 "Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2014 - 2017","Implemented technical imports of the SAT, ACT, and other academic test data
files through redesigns and ongoing updates to other academic test imports.",
 "Information Specialist","University of Wisconsin Office of Admissions and Recruitment","2014 - 2017","Represented the Admissions Office in the University-wide Data Integrity Group
to standardize data reporting.",
"Technical Services","Epic","2012 - 2014"," Supported a health care organization through installing, optimizing, and upgrading Epic software. This included planning and overseeing long term projects,
quickly responding to requests and issues that arose, and troubleshooting bugs
in the Epic software.",
"Technical Services","Epic","2012 - 2014","Became an expert on the communication infrastructure needed for Epic’s mobile
applications to connect to our customer’s databases, and lead an effort to change
our recommended server configuration.",
"Technical Services","Epic","2012 - 2014","Developed a handful of bug fixes and enhancements to our ambulatory and handheld software.",
"Cop-op/Intern Research Assistant","LMI","2009 - 2011","Assisted in a review of the Oce of the Undersecretary of Defense for Acquisition,
Technology, and Logistics by interviewing employees, categorizing interviewee
responses, and analyzing them for patterns to contribute to recommendations to
the Oce.",
"Cop-op/Intern Research Assistant","LMI","2009 - 2011","Conducted a comparison of operating and support costs of military materiel gathered from various sources into multiple data systems, and assessed the validity of
the data within those systems",
"Cop-op/Intern Research Assistant","LMI","2009 - 2011"," Assisted a large scale study on the cost of corrosion to the U.S. Department of
Defense by repairing and analyzing large amounts of data.",
"Cop-op/Intern Research Assistant","LMI","2009 - 2011","Designed and created relational database and accompanying user interface to assess and rewrite Product/Service purchasing codes for the United States General
Services Administration."
)%>%
  detailed_entries(role, dates, company,, details)
```

#Volunteer and Other Experience 
```{r}
tribble(
  ~role, ~org, ~dates, ~deets,
  "Membership Committee Secretary","Democratic Party of Dane County","2017 - Present","Interviewed and worked with a number of experienced members of the Democratic Party of Wisconsin to create a presentation to introduce the organizational structure of the Democratic Party to other newcomers, which I then presented
on multiple occasions",
  "Membership Committee Secretary","Democratic Party of Dane County","2017 - Present","Facilitated the planning of multiple community events, several with 100+ attendees",
  "Volunteer","MOSES: Madison Organizing in SOlidarity, Equity, and Strength","2016 - 2017","Helped implement CiviCRM and a new installation of WordPress to help their
efforts in reforming Wisconsin’s prison system",
  "Student","University of Pittsburgh","2007 - 2011","Observed and analyzed patient trac and work flows in the Pittsburgh Veterans Affairs Emergency Department as senior project, culminating in a model of
patient flow and recommended process improvements.",
  "Student","University of Pittsburgh","2007 - 2011","Designed contact database for Urban Youth Action, a non-profit in Pittsburgh that tutors and mentors high schoolers.",
  "Student","University of Pittsburgh","2007 - 2011","Focused on Databases and Computer Science."
)%>%
  detailed_entries(role, dates, org,,deets)
```

# Academic Interests
 * Political Sociology
 * Organizational Sociology
 * Democracy and alternate organizing structures
 * Combating online behavioral modification and manipulation on social media
 * Network Dynamics
 * Poverty, Segregation, and Inequality
 * Trans issues and theory
 * Fascism
 * Sociology of Religion
 
# Personal Interests
 * Flint, Michigan
 * Ukulele, guitar, piano, vocal performance, and music production
 * Knitting
 * Gerdening and sustainable small scale agriculture

