---
name: Everett Trechter
position: "Data Analyst, Student of Public Policy"
address: "Hubert Humphrey - University of Minnesota"
phone: 810.931.6633
profilepic: me.jpg
www: www.everettcarytrechter.com
email: "everett.trechter@gmail.com"
twitter: everett_ct
github: Everett-Trechter
linkedin: Everett Trechter
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I am interested in a career centered on research and analysis in the realm of policy,
political sociology and/or organizational sociology. I am currently looking to gain
analytic skills and a more in depth understanding of research methods, theories and
general knowledge in order to comprehend and help correct the structural inequalities
of our world. My degree in Industrial Engineering with a focus on Information Systems
and Computer Science provides a solid foundation of technical skills and experiences
working with data-driven solutions. In my career I have built on those skills and have
used them to help government agencies, hospital organizations, and most recently the
Oce of Admissions and Recruitment at the University of Wisconsin."
output: 
  vitae::awesomecv
headcolor: 77815c

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```

#Skills
 * Data Analysis (using R)
 * Data Reporting and Visualization (R, Excel, and Tableau)
 * Geographical Information Systems (QGIS and ArcGIS)
 * Relational Database Design and SQL
 * PeopleSoft Query Tools, PeopleTools, PeopleCode
 * Familiar with Java, HTML/CSS, Javascript, Python, and R
 * Skilled with Microsoft Oce Suite, including VBA Macros and MS Access
 * Troubleshooting and creative problem solving
 * Quick learning, speed reading

# Education
```{r}
tribble(
  ~ degree, ~ uni, ~school, ~ dates, ~ details,
  "B.Eng in Industrial Engineering", "University of Pittsburgh","Swanson School of Engineering","2007 - 2011","Magna Cum Laude"
)%>%
  detailed_entries(degree, dates, uni, school, details)
```